Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-06-08 doc/paper.Rmd
added figures from hipergator run with ind-level random effects. #61

```{r size-plot, fig.cap=size_cap, fig.width=7, fig.height=7}
size_plot & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=7.5, fig.width=7}
f_spei_plot & theme(text = element_text(size = 10))
```

>>>>

```{r size-plot, fig.cap=size_cap, fig.width=7, fig.height=7}
# size_plot & theme(text = element_text(size = 10))
include_graphics(here("doc", "figures", "size_plot_ufhpc.png"))
```

@@

```{r flwr-spei, fig.cap=f_spei_cap, fig.height=7.5, fig.width=7}
# f_spei_plot & theme(text = element_text(size = 10))
include_graphics(here("doc", "figures", "f_spei_plot_ufhpc.png"))
```
